A Survey of Quantitative Descriptions of Molecular Structure

### 2012-04-08 paper.tex
More text of descriptors of shape

While molecular surfaces are useful, molecular shape is a key factor
in ligand-receptor interactions. A variety of descriptors have been
devised to characterize molecular shape. For example, the ``shape
signature'' approach described by Zauhar et al \cite{Zauhar:2003fk} is a novel application of a
ray tracing method that generates a description of the molecular
shape. Ballester et al \cite{Ballester:2007aa} described the Ultrafast
Shape Recognition (USR) approach that characterized molecular shape in
terms of the distribution of distances between the atoms and a set of
pre-defined points. As a result, the calculation procedure is
extremely fast and once calculated shape similarities can be evaluated
rapidly via a simple distance calculation. 
\textbf{
  spherical harmonic shape descriptors, field based descriptors
  [Cresset etc]}

>>>>

While molecular surfaces are useful, molecular shape is a key factor
in ligand-receptor interactions. A variety of descriptors have been
devised to characterize molecular shape. The use of overlapping atom
centered Gaussians to represent molecular shape \cite{Grant:1995aa}
represents a significant computational advantage over the traditional
analytical approach of intersecting hard spheres, supporting extremely
rapid shape comparisons \cite{Grant:1999vn}. An alternative approach
described by Ritchie et al \cite{Ritchie:1999kx} employed a spherical
harmonic based representation of surfaces, that in contrast to the
Gaussian approach allows one to generate characterizations of the
surface and hence the shape at varying resolutions. In addition to
functional representations of molecular shape, a number of simpler
formulations have been defined. For example, the ``shape signature''
approach described by Zauhar et al \cite{Zauhar:2003fk} is a novel
application of a ray tracing method that generates a description of
the molecular shape. Ballester et al \cite{Ballester:2007aa} described
the Ultrafast Shape Recognition (USR) approach that characterized
molecular shape in terms of the distribution of distances between the
atoms and a set of pre-defined points. As a result, the calculation
procedure is extremely fast and once calculated shape similarities can
be evaluated rapidly via a simple distance calculation.
